\begin{thebibliography}{00}

\bibitem{b1} Tang W, Weil MH. Cardiac arrest and cardiopulmonary resuscitation. In: Critical Care Medicine. Elsevier; 2008. p. 3–15.

\bibitem{b2}Beane A, Ambepitiyawaduge PDS, Thilakasiri K, Stephens T, Padeniya A, Athapattu P, et al. Practices and perspectives in cardiopulmonary resuscitation attempts and the use of do not attempt resuscitation orders: A cross-sectional survey in Sri Lanka. Indian J Crit Care Med [Internet]. 2017;21(12):865–8. Available from: http://dx.doi.org/10.4103/ijccm.IJCCM\_314\_17
 	 
\bibitem{b3}Abeywardena MY. Dietary fats, carbohydrates and vascular disease: Sri Lankan perspectives. Atherosclerosis [Internet]. 2003;171(2):157–61. Available from: http://dx.doi.org/10.1016/s0021-9150(03)00157-6
 	 
\bibitem{b4}Who.int. [cited 2022 Jun 26]. Available from: https://www.who.int/docs/default-source/gho-documents/world-health-statistic-reports/6-june-18108-world-health-statistics-2018.pdf
 	 
\bibitem{b5}Ye C, Wang O, Liu M, Zheng L, Xia M, Hao S, et al. A real-time early warning system for monitoring inpatient mortality risk: Prospective study using electronic medical record data. J Med Internet Res [Internet]. 2019;21(7):e13719. Available from: http://dx.doi.org/10.2196/13719
 	 
\bibitem{b6}Nishijima I, Oyadomari S, Maedomari S, Toma R, Igei C, Kobata S, et al. Use of a modified early warning score system to reduce the rate of in-hospital cardiac arrest. J Intensive Care [Internet]. 2016;4(1). Available from: http://dx.doi.org/10.1186/s40560-016-0134-7
 	 
\bibitem{b7}Marinkovic O, Sekulic A, Trpkovic S, Malenkovic V, Pavlovic A. The importance of early warning score (EWS) in predicting in-hospital cardiac arrest—Our experience. Resuscitation [Internet]. 2013;84:S85. Available from: http://dx.doi.org/10.1016/j.resuscitation.2013.08.215
 	 
\bibitem{b8}De Silva AP, Sujeewa JA, De Silva N, Rathnayake RMD, Vithanage L, Sigera PC, et al. A retrospective study of physiological observation-reporting practices and the recognition, response, and outcomes following cardiopulmonary arrest in a low-to-middle-income country. Indian J Crit Care Med [Internet]. 2017;21(6):343–5. Available from: http://dx.doi.org/10.4103/ijccm.IJCCM\_136\_17
 	 
\bibitem{b9}Ranawaka UK, Wijekoon CN, Pathmeswaran A, Kasturiratne A, Gunasekera D, Chackrewarthy S, et al. Risk estimates of cardiovascular diseases in a Sri Lankan community. Ceylon Med J [Internet]. 2016;61(1):11–7. Available from: http://dx.doi.org/10.4038/cmj.v61i1.8253
 	 
\bibitem{b10}Beane A, De Silva AP, De Silva N, Sujeewa JA, Rathnayake RMD, Sigera PC, et al. Evaluation of the feasibility and performance of early warning scores to identify patients at risk of adverse outcomes in a low-middle income country setting. BMJ Open [Internet]. 2018;8(4):e019387. Available from: http://dx.doi.org/10.1136/bmjopen-2017-019387
 	 
\bibitem{b11}Smith GB, Prytherch DR, Schmidt PE, Featherstone PI, Higgins B. A review, and performance evaluation, of single-parameter “track and trigger” systems. Resuscitation [Internet]. 2008;79(1):11–21. Available from: http://dx.doi.org/10.1016/j.resuscitation.2008.05.004
 	 
\bibitem{b12}Gerry S, Birks J, Bonnici T, Watkinson PJ, Kirtley S, Collins GS. Early warning scores for detecting deterioration in adult hospital patients: a systematic review protocol. BMJ Open [Internet]. 2017;7(12):e019268. Available from: http://dx.doi.org/10.1136/bmjopen-2017-019268
 	 
\bibitem{b13}Kwon J-M, Lee Y, Lee Y, Lee S, Park J. An algorithm based on deep learning for predicting in-hospital cardiac arrest. J Am Heart Assoc [Internet]. 2018;7(13). Available from: http://dx.doi.org/10.1161/JAHA.118.008678

\bibitem{a14}N. Patki, R. Wedge and K. Veeramachaneni, "The Synthetic Data Vault," 2016 IEEE International Conference on Data Science and Advanced Analytics (DSAA), Montreal, QC, Canada, 2016, pp. 399-410, doi: 10.1109/DSAA.2016.49.

\bibitem{b14}Kim J, Chae M, Chang H-J, Kim Y-A, Park E. Predicting cardiac arrest and respiratory failure using Feasible Artificial Intelligence with Simple Trajectories of patient data. J Clin Med [Internet]. 2019;8(9):1336. Available from: http://dx.doi.org/10.3390/jcm8091336
 	 
\bibitem{b15}Choi E, Schuetz A, Stewart WF, Sun J. Using recurrent neural network models for early detection of heart failure onset. J Am Med Inform Assoc [Internet]. 2017;24(2):361–70. Available from: http://dx.doi.org/10.1093/jamia/ocw112
 	 
\bibitem{b16}Ge W, Huh J-W, Park YR, Lee J-H, Kim Y-H, Turchin A. An interpretable ICU mortality prediction model based on logistic regression and Recurrent Neural Networks with LSTM units. AMIA Annu Symp Proc. 2018;2018:460–9.
 	 
\bibitem{b17}Aczon M, Ledbetter D, Ho L, Gunny A, Flynn A, Williams J, et al. Dynamic mortality risk predictions in pediatric critical care using recurrent neural networks [Internet]. arXiv [stat.ML]. 2017. Available from: http://arxiv.org/abs/1701.06675
 	 
\bibitem{b18}Aleem IS, Schemitsch EH, Hanson BP. What is a clinical decision analysis study? Indian J Orthop [Internet]. 2008;42(2):137–9. Available from: http://dx.doi.org/10.4103/0019-5413.40248
 	 
\bibitem{b19}Bae J-M. The clinical decision analysis using decision tree. Epidemiol Health [Internet]. 2014;36:e2014025. Available from: http://dx.doi.org/10.4178/epih/e2014025
 	 
\bibitem{b20}Myers J, McCabe SJ. Understanding medical decision making in hand surgery. Clin Plast Surg [Internet]. 2005;32(4):453–61, v. Available from: http://dx.doi.org/10.1016/j.cps.2005.05.001
 	 
\bibitem{b21}Podgorelec V, Kokol P, Stiglic B, Rozman I. J Med Syst [Internet]. 2002;26(5):445–63. Available from: http://dx.doi.org/10.1023/a:1016409317640
 	 
\bibitem{b22}Kurniawan LB, Bahrun U, Mangarengi F, Darmawati ER, Arif M. Blood urea nitrogen as a predictor of mortality in myocardial infarction. Zinc suppl improv heme biosynth rats expo lead [Internet]. 2013 [cited 2022 Jun 26];32(3):172–8. Available from: https://univmed.org/ejurnal/index.php/medicina/article/view/91

\bibitem{a23}R. van den Goorbergh, M. van Smeden, D. Timmerman, and B. Van Calster, “The harm of class imbalance corrections for risk prediction models: illustration and simulation using logistic regression,” J. Am. Med. Inform. Assoc., vol. 29, no. 9, pp. 1525–1534, 2022, Available from: https://doi.org/10.1093/jamia/ocac093.

\bibitem{b23}Kughapriya P, Ponnudhali D, Jones E. Evaluation of serum electrolytes in Ischemic Heart Disease patients [Internet]. Njbms.in. [cited 2022 Jun 26]. Available from: http://njbms.in/uploads/19/1564\_pdf.pdf
 	 
\bibitem{b24}Tan BY, Judge DP. A clinical approach to a family history of sudden death. Circ Cardiovasc Genet [Internet]. 2012;5(6):697–705. Available from: http://dx.doi.org/10.1161/CIRCGENETICS.110.959437
 	 
\bibitem{b25}Mukaka MM. Statistics corner: A guide to appropriate use of correlation coefficient in medical research. Malawi Med J. 2012;24(3):69–71.
 	 
\bibitem{b26}Kim J, Park YR, Lee JH, Lee J-H, Kim Y-H, Huh JW. Development of a real-time risk prediction model for in-hospital cardiac arrest in critically ill patients using deep learning: Retrospective study. JMIR Med Inform [Internet]. 2020;8(3):e16349. Available from: http://dx.doi.org/10.2196/16349
 	 
\bibitem{b27}Medlej K. National Early Warning Score (NEWS) [Internet]. MDCalc. [cited 2022 Jun 26]. Available from: https://www.mdcalc.com/national-early-warning-score-news
 	 
\bibitem{b28}Medlej K. Modified Early Warning Score (MEWS) for clinical deterioration [Internet]. MDCalc. [cited 2022 Jun 26]. Available from: https://www.mdcalc.com/modified-early-warning-score-mews-clinical-deterioration
 	 
\bibitem{b29}CART (Cardiac Arrest Risk Triage) Score [Internet]. MDCalc. [cited 2022 Jun 26]. Available from: https://www.mdcalc.com/cart-cardiac-arrest-risk-triage-score
 	 
\bibitem{b30}van der Ploeg T, Austin PC, Steyerberg EW. Modern modelling techniques are data hungry: a simulation study for predicting dichotomous endpoints. BMC Med Res Methodol [Internet]. 2014;14(1):137. Available from: http://dx.doi.org/10.1186/1471-2288-14-137
 	 
\bibitem{b31}Tonekaboni S, Laussen P, Eytan D, Greer R, Goodfellow SD, Goodwin A, et al. Prediction of cardiac arrest from physiological signals in the pediatric ICU [Internet]. Squarespace.com. [cited 2022 Jun 26]. Available from: \url{https://static1.squarespace.com/static/59d5ac1780bd5ef9c396eda6/t/5b73738d88251beb6017ede8/1534343143656/Tonekaboni\_S}
 	 
\bibitem{b32}Mehmood A, Iqbal M, Mehmood Z, Irtaza A, Nawaz M, Nazir T, et al. Prediction of heart disease using deep convolutional neural networks. Arab J Sci Eng [Internet]. 2021;46(4):3409–22. Available from: http://dx.doi.org/10.1007/s13369-020-05105-1
 	 
\bibitem{b33}Li H, Wu TT, Yang DL, Guo YS, Liu PC, Chen Y, et al. Decision tree model for predicting in-hospital cardiac arrest among patients admitted with acute coronary syndrome. Clin Cardiol [Internet]. 2019;42(11):1087–93. Available from: http://dx.doi.org/10.1002/clc.23255



\end{thebibliography}